Figures

### 2020-03-20 manuscript/figures.Rmd
move heatmap to appendix

```{r metric_correlations, fig.cap = "Pearson correlation coefficients of map-derived metrics against inlake slope and deepest point distance metrics.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', out.width="11cm", fig.align='center'}
knitr::include_graphics("../figures/metric_correlations-1.pdf")
```

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r depth_model_metrics, fig.cap = "Table 2: Model fit and predictive accuracy metrics for all combinations of true (inlakeslope, distdeepest) and proxy (slopemean, distviscenter) metrics. Tiles are colored by their R2 values and labeled with their RMSE values.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/depth_model_metrics-1.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{5}

@@

>>>>

```{r depth_model_metrics, fig.cap = "Model fit and predictive accuracy metrics for all combinations of true (inlakeslope, distdeepest) and proxy (slopemean, distviscenter) metrics. Tiles are colored by their R2 values and labeled with their RMSE values.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/depth_model_metrics-1.pdf")
```

@@

```{r metric_correlations, fig.cap = "Pearson correlation coefficients of map-derived metrics against inlake slope and deepest point distance metrics.", warning=FALSE, echo = FALSE, eval=TRUE, out.width="11cm", fig.align='center', out.extra=''}
knitr::include_graphics("../figures/metric_correlations-1.pdf")
```
